PM Component Paper Plots

### 2021-02-07 code/data-processors/air-data-processor.Rmd
function for forest plots for results

```{r load packages}
library(tidyverse)
library(here)
#library(lubridate)
#library(naniar) # for replacing -999 with NA
```

@@

dt.aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
  filter(
    #remove monitors closed before 2000
    year(as.Date(Site.Closed.Date)) >= 2000 | Site.Closed.Date == "",
    !State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
                       "Guam", "Country Of Mexico","Canada") 
    #remove non-CONUS states
    ) %>%  
  transmute(
    Site.ID = as.factor(sprintf(
      "%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
                                as.numeric(as.character(State.Code)),
                                County.Code, Site.Number)), 
    State.Code = as.factor(sprintf("%02d", as.numeric(as.character(State.Code)))),
    County.Code = as.factor(sprintf("%03d", County.Code)),
    Latitude,
    Longitude, 
    State = state.abb[match(State.Name,state.name)],
    State = as.factor(ifelse(State.Name == "District Of Columbia","DC", State)),
    Land.Use,
    Location.Setting = as.factor(
      ifelse(Location.Setting == "URBAN AND CENTER CITY", "URBAN",
             as.character(Location.Setting)))
    ) %>% 
  merge(dt.state.region[, c("State", "Region.IV")]) %>% 
  arrange(Site.ID)

@@

dt.aqs.sites %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n())
```

@@

ec.c %>% merge(dt.aqs.sites) %>% 
  distinct(Site.ID, Location.Setting) %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n()) # > Urban and Suburban

@@

oc.c %>% merge(dt.aqs.sites) %>% 
  distinct(Site.ID, Location.Setting) %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n()) # > Urban and Suburban

@@

dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 558 > 471 > 322
  merge(dt.aqs.sites)
save(dt.site.pmc, file = here('data', 'processed', 'site-pmc.RDa'))

@@

```{r Post mergeing with CMS Data}
dt.pmc.site.ndi <- read.csv(here('data', 'processed', 'site_pmc_ndi.csv')) %>% 
  rename(Site.ID = Site_ID) %>% 
  left_join(dt.aqs.sites) %>% 
  left_join(dt.site.carbon.method)
# 317 out of 320 sites have population living in their 12-mile bufferzone

@@

dt.pmc.site.ndi.bz6 <- read.csv(here('data', 'processed', 'site_pmc_ndi_bz6.csv')) %>% 
  rename(Site.ID = Site_ID) %>% 
  left_join(dt.aqs.sites)

>>>>

```{r load packages}
library(tidyverse)
library(here)
library(lubridate)
#library(naniar) # for replacing -999 with NA
```

@@

dt.aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
  filter(
    #remove monitors closed before 2000
    year(as.Date(Site.Closed.Date)) >= 2000 | Site.Closed.Date == "",
    !State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
                       "Guam", "Country Of Mexico","Canada") 
    #remove non-CONUS states
    ) %>%  
  transmute(
    Site.ID = as.factor(sprintf(
      "%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
                                as.numeric(as.character(State.Code)),
                                County.Code, Site.Number)), 
    State.Code = as.factor(sprintf("%02d", as.numeric(as.character(State.Code)))),
    County.Code = as.factor(sprintf("%03d", County.Code)),
    Latitude,
    Longitude, 
    State = state.abb[match(State.Name,state.name)],
    State = as.factor(ifelse(State.Name == "District Of Columbia","DC", State)),
    Land.Use,
    Location.Setting
    ) %>% 
  merge(dt.state.region[, c("State", "Region.IV")]) %>% 
  arrange(Site.ID)

@@

dt.aqs.sites %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n())

dt.aqs.sites.ii <- dt.aqs.sites %>% 
  mutate(Location.Setting = as.factor(
      ifelse(Location.Setting == "URBAN AND CENTER CITY", "URBAN",
             as.character(Location.Setting))))

save(dt.aqs.sites.ii, file = here('data', 'processed', 'aqs-sites-ii.RDa'))
```

@@

ec.c %>% merge(dt.aqs.sites.ii) %>% 
  distinct(Site.ID, Location.Setting) %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n()) # > Urban and Suburban

@@

oc.c %>% merge(dt.aqs.sites.ii) %>% 
  distinct(Site.ID, Location.Setting) %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n()) # > Urban and Suburban

@@

dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 558 > 471 > 322
  merge(dt.aqs.sites.ii)
save(dt.site.pmc, file = here('data', 'processed', 'site-pmc.RDa'))

@@

```{r Post mergeing with CMS Data}
dt.pmc.site.ndi <- read.csv(here('data', 'processed', 'site_pmc_ndi.csv')) %>% 
  rename(Site.ID = Site_ID) %>% 
  left_join(dt.aqs.sites.ii) %>% 
  left_join(dt.site.carbon.method)
# 317 out of 320 sites have population living in their 12-mile bufferzone

@@

dt.pmc.site.ndi.bz6 <- read.csv(here('data', 'processed', 'site_pmc_ndi_bz6.csv')) %>% 
  rename(Site.ID = Site_ID) %>% 
  left_join(dt.aqs.sites.ii)

### 2021-02-07 code/data-viz/forest-plots.Rmd
function for forest plots for results

```{r Call Functions}
source(here('code','data-viz','plot-functions.R'))
```

@@

```{r set theme 2 - effect modification, subgroups, multiple groups plots}
ggtheme.multi.1 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r set theme 3 - effect modification, subgroups, multiple groups plots}
ggtheme.multi.2 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-region.png'), width = 6.5, height = 7.5)
```
```{r - Factor Region}
data <- out.fac.region %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
  Tag = ifelse(Region == "west", "d",
               ifelse(Region == "midwest", "c",
                      ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
  )

>>>>

```{r Call Functions}
source(here('code','data-viz','forest-plot-functions.R'))
```

@@

```{r set theme 2 - components - effect modification, subgroups, multiple groups plots}
ggtheme.multi.1 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r set theme 3 - factors - effect modification, subgroups, multiple groups plots}
ggtheme.multi.2 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

@@

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
ggsave(here('output', 'plot','pmc-region.png'), width = 6.5, height = 7.5)
```

```{r - Factor Region}
data <- out.fac.region %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
  Tag = ifelse(Region == "west", "d",
               ifelse(Region == "midwest", "c",
                      ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
  )
